\section{Professional Employment}
\cventry{2018-Present}{University of California San Diego}{PhD Candidate}{San Diego, CA}{}{Advisor: Nadia Polikarpova. Graduate research in programming languages and artificial intelligence.}
%
\cventry{2023-Present}{RISE, Microsoft Research}{Part-time Researcher}{Redmond, WA}{}
{Collaborators: Christian Poelitz, Andrew Gordon, Ben Zorn, Jack Williams, José Cambronero, Carina Negreanu.
Project (Ongoing): Generation of synthetic tabular data for LLMs that provides differential privacy guarantees.}
%  
\cventry{Fall 22--Winter 23}{Google X - the moonshot factory}{PhD Resident, Pitchfork}{Mountain View, CA}{}
{Collaborators: Joel Galenson, Jonathan Malmaud, Rishabh Singh. Project (details confidential): Automatic code migration system driven by LLMs that upgrades deprecated library code and translates across languages.}
%
\cventry{Summer 2022}{Calc Intelligence Team, Microsoft Research}{Graduate Research Intern}{Cambridge, UK (Remote)}{}{Collaborators: Christian Poelitz, Andrew Gordon, Ben Zorn, Jack Williams, José Cambronero, Carina Negreanu. Project: CodeXData, a system that synthesizes  spreadsheet manipulation programs over tabular data from natural-language description and explores LLM-based code generation for data-centric tasks. Resulted in a paper submission and the filing of a patent.}
%
\cventry{Summer 2019}{PROSE, Microsoft Research}{Graduate Research Intern}{Redmond, WA}{}{Collaborators: Alan Leung, Arjun Radhakrishnan, Gustavo Soares.
Project: Extension of BluePencil, an on-the-fly synthesis engine that automatically detects repetitive edits and synthesizes transformations for other locations in the code, based on only one instance of the edit. Resulted in an OOPSLA paper, and a US patent.}
%
\cventry{Summer 2017}{Technische Universität Kaiserslautern}{Student Researcher}{Kaiserslautern, Germany}{}
{Collaborators: Annette Bieniusa and Peter Zeller.
Project: Extension of Repliss, a formal verification system that supports conflict resolution data types (CRDTs) to manage the state of replicas and guarantee safety of applications built on weakly consistent databases. Developed a collaborative editing application as a testing prototype for Antidote, a distributed database with replicated data types.}
%
\cventry{Summer 2016}{Tata Institute of Fundamental Research}{Undergraduate Research Intern}{Mumbai, India}{}{Collaborators: Ashutosh Gupta. Bachelor's Thesis Project: A fence synthesis system for weak memory models that uses a constraint-based approach to guarantee minimal number of inserted fences. Evaluated the tool, Orbis against state of the art fence synthesis tools (Glue and Memorax) and achieved optimal fence placement.}
%
\cventry{Winter 2015}{Outreachy, Linux Kernel}{Software Development Intern}{Remote}
{}{Collaborators: Greg Hartman. Project: Linux kernel staging drivers cleanup, contributed over 500 patches to kernel code that involved updating API interfaces and fixing bugs using static analysis tools, Coccinelle and Checkpatch. Ranked 6\textsuperscript{th} among the most active developers in terms of patches for 4.4 Linux version by LWN.net.}