\section{Peer-reviewed Publications}
\subsection{Published Conference Papers}
\cvline{OOPSLA 2023}{\textbf{Shraddha Barke}\textsuperscript{*}, Michael James\textsuperscript{*}, Nadia Polikarpova. Grounded Copilot: How Programmers Interact with Code-Generating Models. \emph{Object-Oriented Programming, Systems, Languages, and Applications}, 2023.}{}
%
\cvline{OOPLSA 2021}{Kasra Ferdowsi, \textbf{Shraddha Barke}, Hila Peleg, Nadia Polikarpova, Sorin Lerner. LooPy: Interactive Program Synthesis with Control Structures. \emph{Object-Oriented Programming, Systems, Languages, and Applications}, 2021.}{}
%
\cvline{OOPSLA 2020}{\textbf{Shraddha Barke}, Hila Peleg, Nadia Polikarpova. Just-in-Time Learning for Bottom-Up Enumerative Synthesis. \emph{Object-Oriented Programming, Systems, Languages, and Applications}, 2020.}{}
%
\cvline{OOPSLA 2020}{Xiang Gao\textsuperscript{*}, \textbf{Shraddha Barke}\textsuperscript{*}, Arjun Radhakrishna, Gustavo Soares, Sumit Gulwani, Alan Leung, Nachiappan Nagappan, Ashish Tiwari. Feedback-Driven Semi-Supervised Synthesis of Program Transformations. \emph{Object-Oriented Programming, Systems, Languages, and Applications}, 2020.}{}
%
\cvline{EMNLP 2019}{\textbf{Shraddha Barke}, Rose Kunkel, Eric Meinhardt, Nadia Polikarpova, Eric Bakovic, and Leon Bergen. Constraint-based Learning of Phonological Processes. \emph{Conference on Empirical Methods in Natural Language Processing}, 2019.}{}
%
\subsection{Book Chapters}
\cvline{2018}{Annette Bieniusa, Peter Zeller, and \textbf{Shraddha Barke}. Collaborative Work Management with a Highly-Available Kanban Board. \emph{Principled Software Development - Essays Dedicated to Arnd Poetzsch-Heffter on the Occasion of his 60th Birthday}, 2018.}{}
%
\subsection{In Submission/ Under Preparation Papers}
\cvline{ASE 2023}{\textbf{Shraddha Barke}, Christian Poelitz, Carina Suzana Negreanu, Benjamin Zorn,  José Cambronero, Andrew D. Gordon, Vu Le, Elnaz Nouri, Nadia Polikarpova, Advait Sarkar, Brian Slininger, Neil Toronto, Jack Williams. CodeXData: Solving Data-Centric Tasks with Large Language
  Models}
%
\cvline{2019}{John Sarracino, \textbf{Shraddha Barke},  Hila Peleg, Nadia Polikarpova, and Sorin Lerner. Targeted  Program  Synthesis  for  Programming  with  Invariants.}
